Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2019-10-06 manuscript/manuscript.tex
changes

While the presence of positive temporal covariances is consistent with linked
selection affecting allele frequencies over time, this measure not easily
interpretable. Additionally, we can quantify the impact of linked selection on
allele frequency change as the ratio of total covariance in allele frequency
change to the total variance in allele frequency change. We denote the
change in allele frequency as $\Delta p_t = p_{t+1}-p_t$, where $p_t$ is the
allele frequency in generation $t$. Since the total variation in allele
frequency change can be partitioned into variance and covariance components,
$\var(p_t - p_0) = \sum_{i} \var(\Delta p_i) + \sum_{i \ne j} \cov(\Delta
p_i, \Delta p_j)$, and the covariances are zero when drift acts alone, this is
a lower bound on how much of the variance in allele frequency change is caused
by linked selection \parencite{Buffalo2019-io}. We call this measure $G(t)$, defined as

\begin{align}
  G(t) = \frac{\sum_{i\ne j}^t \cov(\Delta p_i, \Delta p_j)}{\var(p_t - p_0)}
\end{align}
%
which estimates the effect of linked selection between the initial
generation $0$ and some later generation $t$, which can be varied to see how
this quantity grows through time. As with the temporal covariances, the study
design of \textcite{Barghi2019-qy} leads our measure $G(t)$ to be even more
conservative, since the temporal covariances within each ten-generation block
between sequenced timepoints are not directly observable, and are not included
in the numerator of $G(t)$. Still, we find a remarkably strong signal.
Greater than $20\%$ of total variation in allele frequency change over 60
generations is the result of linked selection.

@@

\vb{We note that blah blha lbah, have a look at the pairwiwe covariances for
Fig 2A}

>>>>

While the presence of positive temporal covariances is consistent with 
\gc{selection} affecting allele frequencies over time, this measure not easily
interpretable. \gc{We can calculate a more intuitive measure from this
number to} quantify the impact of \gc{selection} on
allele frequency change as the ratio of total covariance in allele frequency
change to the total variance in allele frequency change. We denote the
change in allele frequency as $\Delta p_t = p_{t+1}-p_t$, where $p_t$ is the
allele frequency in generation $t$. Since the total variation in allele
frequency change can be partitioned into variance and covariance components,
$\var(p_t - p_0) = \sum_{i} \var(\Delta p_i) + \sum_{i \ne j} \cov(\Delta
p_i, \Delta p_j)$, and the covariances are zero when drift acts alone, this is
a lower bound on how much of the variance in allele frequency change is caused
by linked selection \parencite{Buffalo2019-io}. We call this measure $G(t)$, defined as

\begin{align}
  G(t) = \frac{\sum_{i\ne j}^t \cov(\Delta p_i, \Delta p_j)}{\var(p_t - p_0)}
\end{align}
%
which estimates the effect of \gc{selection on allele frequency
  change} between the initial
generation $0$ and some later generation $t$, which can be varied to see how
this quantity grows through time. As with the temporal covariances, the study
design of \textcite{Barghi2019-qy} leads our measure $G(t)$ to be even more
conservative, since the temporal covariances within each ten-generation block
between sequenced timepoints are not directly observable, and are not included
in the numerator of $G(t)$. Still, we find a remarkably strong signal.
Greater than $20\%$ of total\gc{, genome-wide allele frequency
  change} over 60 %variation in
generations is the result of selection.

@@

\vb{We note that blah blha lbah, have a look at the pairwiwe covariances for
Fig 2A} \gc{THIS IS about double checking that that last time point is
about right?}
